\documentclass[12pt]{article}
\usepackage{xcolor} % for different colour comments
\usepackage[left=15mm,right=15mm,top=0.6in,bottom=0.5in]{geometry}

%% Comments
\newif\ifcomments\commentsfalse %i replaced comments true by comment false so the comments will be hidden

\ifcomments
\newcommand{\authornote}[3]{\textcolor{#1}{[#3 ---#2]}}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\else
\newcommand{\authornote}[3]{}
\newcommand{\todo}[1]{}
\fi

\newcommand{\wss}[1]{\authornote{magenta}{SS}{#1}}
\newcommand{\hm}[1]{\authornote{blue}{HM}{#1}} %Hediyeh
\newcommand{\tz}[1]{\authornote{blue}{TZ}{#1}} %Tahereh
\newcommand{\pl}[1]{\authornote{blue}{PL}{#1}} %Peng



\setlength{\headsep}{-20pt}
\setlength{\footskip}{0pt}
\begin{document}
\title{newAGEtech, Group H }
\author{Genevieve Okon (Okong), Abraham Omorogbe(Omorogoa),\\
 Eric Le Forti(Leforte)}
\maketitle


\section*{Project Drivers}

\subsection*{1. THE PURPOSE OF THE PROJECT}

\subsection*{1.A) The User Business or Background of the Project}
This project will be an attempt to ease the difficult and tedious process of verifying a website’s current status and state of availability as well as also being able to assist researchers in scouring the web efficiently for potentially relevant sources of data. Some specific tasks expected to be completed using this software include ensuring all of a website’s pages are functioning correctly and resources that should be available are, data mining for certain research topics and for security professionals ensuring that only the webpages that should be visible are.

\subsection*{1.B) Goals of the Project}
This product aims to be used as an effective tool dealing with various forms of website analysis. It will be an efficient and customizable resource that allows you to perform various web crawler based activities on websites in order to increase productivity and for businesses to save money.


\subsection*{2. CLIENTS, CUSTOMERS, STAKEHOLDERS}

\subsection*{2.A) The Client}
The clients of this product will primarily be analysts and website developers.

\subsection*{2.B) The Customer}
The customers of this product will be the companies who employ the aforementioned clients as well as the clients themselves if it is purchased for personal use.

\subsection*{2.C) Other Stakeholders}
The other stakeholders include the developers of the software, investors as well as a previously established application store (i.e. Google Play or Apple’s App Store) for distribution.

\subsection*{3. USERS OF THE PRODUCT}

\subsection*{3.A) The Hands-On Users of the Product}
- Software Developers/Testers
- Develops, tests and maintains websites.
- Strong knowledge of technology, especially technology involved in this product’s field.
- Reasonably educated (most likely a college degree or better).
- Anticipated age group: 20+

Researchers
- Researches various topics relevant to their business, especially matters pertaining to the stock trade.
- No required technological knowledge other than the basics of how to use a computer.
- Expected education is a high school diploma or better
- Anticipated age group: 20+

Other Members of the General Population
- May have any sort of experience, education and skill sets
- Anticipated age group: 10+


\subsection*{3.B) Priorities Assigned to Users}
Key Users:
- Software Developers/Testers
- Researchers

Secondary Users:
N/A

Unimportant Users:
- Other Members of the General Population

\subsection*{3.C) User Participation}
Software Developers:
N/A

Researchers:
- It would be mutually beneficial to obtain a set of desired functionalities that would assist this user in utilizing this product.

Other Members of the General Population:
N/A

\subsection*{3.D) Maintenance Users and Service Technicians}
N/A


\section*{Project Constraints}

\subsection*{4. MANDATED CONSTRAINTS}

\subsection*{4.A) Solution Constraints}
	This project will be implemented using the Python programming language. This is due to the language’s simplicity and available libraries related to the project.

\subsection*{4.B) Implementation Environment of the Current System}
This product will be installed onto a computer system using any platform that accepts the use of Python and will utilize the architecture of the world wide web.

\subsection*{4.C) Partner or Collabrative Applications}
This product will be capable of operating on websites that are locally stored.

\subsection*{4.D) Off-The-Shelf Software}
Some example of similar existing solutions include search engines (i.e. Google or Bing), and various other generic web crawlers that have already been implemented.

\subsection*{4.E) Anticipated Workplace Environment}
This project is expected to be utilized primarily in office environments. These will include a computer that is likely hooked up to an active internet connection.

\subsection*{4.F) Schedule Constraints}
This project must be completed by the eleventh of November.

\subsection*{4.G) Budget Constraints}
The budget for this project is exactly $0.


\subsection*{5. NAMING CONVENTIONS & DEFINITIONS}

\subsection*{5.A) Definition of All Terms, Including Acronyms, Used in the Project}
Web Crawler/Crawler - An internet bot which systematically browses the World Wide Web, typically for the purpose of Web indexing.

Uniform Resource Locator (URL) - A reference (address) to a resource on the internet. Has two main components: a Protocol Identifier (e.g. http) and a Resource Name (e.g. Google.ca)

HyperText Markup Language (HTML) - The standard markup language used to create webpages.

List of standard HTTP status codes and their definitions:

1XX are informational status codes.

Continue (100) - The client should continue with its request.

Switching Protocols (101) - The server has acknowledged and approved a request to switch protocols.

2xx refers to successful requests.

OK (200) - The request has succeeded.

Created (201) - The request succeeded and resulted in a new resource being created.

Accepted (202) - The request has been approved but is still processing.

Non-Authoritative Information (203) - The returned metadata in the entity-header is not the definitive set defined in the origin server, instead it is gathered from a local or third-party copy.

No Content (204) - Request succeeded but no entity-body was required from the server.

Reset Content (205) - Request succeeded, the document view which caused the request to be sent should be updated.

Partial Content (206) - Partial GET request succeeded.

3xx refers to redirection status codes.

Multiple Choices (300) - The requested resource corresponds to any one of a set of representations.

Moved Permanently (301) - The requested resource has been assigned a new permanent URL.

Found (302) - The requested resource currently resides in a temporary location.

See Other (303) - The response to the request can be found under a different URL and should be retrieved using a GET method on that resource.

Not Modified (304) - The client performed a conditional GET request but the document has not been modified.

Use Proxy (305) - The requested resource must be accessed through the proxy given by the Location field.

(306) - No longer in use, the code is now reserved.∂

Temporary Redirect (307) - The requested resource temporarily resides under a different URL.

4xx refers to Client Error status codes.

Bad Request (400) - The request was not understood due to malformed syntax.

Unauthorized (401) - The request requires user authorization.

Payment Required (402) - Code reserved for future use.

Forbidden (403) - The request was understood however, the server is refusing to fulfill it.

Not Found (404) - The server could not find anything matching the provided URL.

Method Not Allowed (405) - The method specified in the Request-Line is not allowed for the resource identified by the Request-URI.

Not Acceptable (406) - The resource identified by the request is only capable of generating response entities which have content characteristics not acceptable according to the accept headers sent in the request.

Proxy Authentication Required (407) - Similar to 401 except the client must first authenticate itself with the proxy.

Request Timeout (408) - The client did not produce a request within the time that the server was prepared to wait.

Conflict (409) - The request could not be completed due to a conflict with the current state of the resource.

Gone (410) - The requested resource is no longer available at the server and no forwarding address is known.

Length Required (411) - The server refuses to accept the request without a defined content length.

Precondition Failed (412) - The precondition given in one or more of the request header fields evaluated to false when it was tested on the server. 

Request Entity Too Large (413) - The server is refusing to process a request because the request entity is larger than the server is willing or able to process.

Request URL Too Long (414) - The server is refusing to service the request because the request URI is longer than the server is willing to interpret.

Unsupported Media Type (415) - The server is refusing to service the request because the entity of the request is in a format not supported by the requested resource for the requested method.

Requested Range Not Satisfiable (416) - A request included a range request header field and none of the range-specifier values in this field overlap the current extent of the selected resource and the request did not include and if-range request header field.

Expectation Failed (417) - The expectation given in an expect request header field could not be met by this server

5xx refers to Server Error status codes.

Internal Server Error (500) - The server encountered an unexpected condition which prevented it from fulfilling the request.

Not Implemented (501) - The server does not support the functionality required to fulfill the request.

Bad Gateway (502) - The server, while acting as a gateway or proxy, received an invalid response from the upstream server it accessed in attempting to fulfill the request.

Service Unavailable (503) - The server is currently unable to handle the request due to a temporary overloading or maintenance of the server.

Gateway Timeout (504) - The server, while acting as a gateway or proxy, did not receive a timely response from the upstream server specified by the URL it needed to access in attempting to complete the request.

HTTP Version Not Supported (505) - The server does not support, or refuses to support, the HTTP protocol version that was used in the request message.

\subsection*{5.B) Data Dictionary for Any Included Models}
This section to be updated as relevant models arise.

\subsection*{6. RELEVANT FACTS & ASSUMPTIONS}

\subsection*{6.A) Facts}
The existing solution is 7,000 lines of Python code.

\subsection*{6.B) Assumptions}
This product assumes that the operational environment supports the execution of Python code.
This product will assume that the HTML code being parsed for links uses correct syntax (otherwise the error messages may be nonsensical).

\noindent \wss{This is an example comment.  You can turn comments off by replacing
  commentstrue by commentsfalse.}\\
\hm{Sample comment}\\
\tz{Sample comment}\\
\pl{Sample comment}

\end{document}

